Audiovisual Analytics of social linked data

### 2017-11-20 latex/nuvem/nuvem1.tex
retoques no nuvem1

\title{Analytic consideration of the society by itself}

@@

\begin{abstract}
Social participation has been growing on the last decade despite
the recent rise of conservative political parties 
in various locations of the world.
We aim to consider a set of developments on linked social data
and analysis performed over the last years, with a focus
on the potential use for the civil society and scientific academy.
Various conceptualizations have been gathered by interviewing specialists
and State authorities and have been validated by them and their institutions.
Data from known social networks, such as Facebook, Twitter, IRC and Email,
and from more specialized social participation platforms, have been
	translated to RDF and linked to these conceptualizations in the form of OWL ontologies~\cite{losd,pnud5}.
Social networks were reported as very stable and their language varies
	with connectivity~\cite{tese,stab}.
	Also, resources recommendation and experiments have been performed with such data.
	How are we to articulate the gathering and analysis 
	of such data with the needs of the civil society and the academy?
	Will it be valuable to deal with the private and State interests
	that shape our society?
	Does Anthropological Physics yield reasonable strategies
	to collect and analyze data from our social structures?
	How does the global semantic web of linked data~\cite{losd}
	relate to linked social data?
\end{abstract}

@@

>>>>

\title{Analytic consideration of the society by itself}
ANALYTIC CONSIDERATION OF THE SOCIETY BY ITSELF

@@

\begin{abstract}
We aim to consider a set of developments on linked social data
and analyses performed over the last years, with a focus
on the potential use for the civil society and scientific academy.
Various conceptualizations have been gathered by interviewing specialists
and State authorities and have been validated by them and their institutions.
Data from known social networks, such as Facebook, Twitter, IRC and Email,
and from more specialized social participation platforms, have been
	translated to RDF and linked to these conceptualizations in the form of OWL ontologies~\cite{losd,pnud5}.
Social networks were reported as very stable and their language varies
	with connectivity~\cite{tese,stab}.
	Also, resources recommendation and experiments have been performed with such data.
	How are we to articulate the gathering and analysis 
	of such data with the needs of the civil society and the academy?
	Will it be valuable to deal with the private and State interests
	that shape our society?
	Does Anthropological Physics yield reasonable strategies
	to collect and analyze data from our social structures?
	How does the global semantic web of linked data~\cite{losd}
	relate to linked social data?
\end{abstract}

@@

\subsection{Acknowledgments}
FAPESP (project 2017/05838-3); ICMC/USP and UFABC researchers;
the open source and free software communities that
made these developments possible.

### 2017-11-20 latex/nuvem/nuvem2.tex
retoques no nuvem1

\author{Renato Fabbri$^1$\\
	Marilia M. Pisani$^2$
}
\address{$^1$IFSC/USP, $^2$CCNH/UFABC}
\email{$^1$renato.fabbri@gmail.com, $^2$marilia.m.pisani@gmail.com}

@@

\subsection{Perceptual framework}
Frequency and intensity are related to pitch and volume
through the Weber-Fechner law.
One might also think about durations on the same sense.
Visual stimuli, on the other hand, seem to be 
more often modeled by the Steven's law (is this true?).
Is it possible to relate frequency and intensity to
pitch and loudness through Steven's law?
Is the perception of visual cues also fit by Weber-Fechner?
The Steven's law is a power law while Weber-Fechner is an exponential
law:
\begin{equation}
	\Delta p = log_X(e_1/e_0)
\end{equation}
\noindent for Weber-Fechner and
\begin{equation}
	p = k.e_1^\alpha
\end{equation}
\noindent for Steven's,
where p is the (subjective) magnitude of the perceived stimuli,
$X$ and $\alpha$ depend on the stimuli,
and $e_0$ and $k$ depend on the the units used.
$\Delta p$ is an interval, a distance, in the perceived magnitude.
$x$, $\alpha$, $e_0$ and $k$ are usually considered constants.

@@

\subsection{Other: Erdös Sectioning, KS-derived statistics, Wordnet,
text mining, stability and differentiation, partnerships}
Other works, such as the classification of participants (vertices) as
hubs, intermediary and peripheral; statistical tests e.g. to
observe linguistic differences among the network participants;
the use of Wordnet and token-oriented methods for text mining;
and current partnership with researchers in physics, computer science,
mathematics, philosopy and social sciences, clinical and social psychology,
give some of the support for our endeavors.~\cite{tese}

@@

With the research groups @Nuvem, 
especially those audiovisual and societal,
we might relate the missing concepts in AAVO,
or enhance the software design of the system;
try to find more about the right tools for visualizing
ontologies and social data.
about pertinent analysis methods
and known conceptualizations.
@Nuvem researchers might want to formalize their own conceptualizations,
and concepts related to AAVO might have similar developments
or be confluent (e.g. symbiotic)
with Section~\ref{current}: software,
theoretical framework, research and institutional experiments and equipment,
linked data, and other initiatives or knowledge.

>>>>

\author{Renato Fabbri$^1$\\
	Marilia M. Pisani$^2$\\
	Maria Cristina Ferreira de Oliveira$^3$
}
\address{$^{1,3}$IFSC/USP, $^2$CCNH/UFABC}
\email{$^1$renato.fabbri@gmail.com, $^2$marilia.m.pisani@gmail.com,
$^3$cristina@icmc.usp.br}

@@

\subsection{Perceptual framework}\label{perceptual}
Frequency and intensity are related to pitch and volume
through the Weber-Fechner law.
One might also think about durations on the same sense.
Visual stimuli, on the other hand, seem to be 
more often modeled by the Steven's law (is this true?).
Is it possible to relate frequency and intensity to
pitch and loudness through Steven's law?
Is the perception of visual cues also fit by Weber-Fechner?
The Steven's law is a power law while Weber-Fechner is an exponential
law:
\begin{equation}
	\Delta p = log_X(e_1/e_0)
\end{equation}
\noindent for Weber-Fechner and
\begin{equation}
	p = k.e_1^\alpha
\end{equation}
\noindent for Steven's,
where p is the (subjective) magnitude of the perceived stimuli,
$X$ and $\alpha$ depend on the stimuli,
and $e_0$ and $k$ depend on the the units used.
$\Delta p$ is an interval, a distance, in the perceived magnitude.
$x$, $\alpha$, $e_0$ and $k$ are usually considered constants.

@@

\subsection{Other: Erdös Sectioning, KS-derived statistics, Wordnet,
text mining, stability and differentiation, partnerships}\label{other}
Other works, such as the classification of participants (vertices) as
hubs, intermediary and peripheral; statistical tests e.g. to
observe linguistic differences among the network participants;
the use of Wordnet and token-oriented methods for text mining;
and current partnership with researchers in physics, computer science,
mathematics, philosopy and social sciences, clinical and social psychology,
give some of the support for our endeavors.~\cite{tese}

@@

With the research groups @Nuvem, 
especially with those more related to audiovisual and social issues,
we might relate the missing concepts in AAVO,
or enhance the software design of the system;
try to find more about the right tools for visualizing
ontologies and social data, or about
pertinent analysis methods and known conceptualizations.
@Nuvem researchers might want to formalize their own conceptualizations,
and concepts related to AAVO might have similar developments
or be confluent (e.g. symbiotic)
with Section~\ref{current}: software,
theoretical framework, research and institutional experiments and equipment,
linked data, and other initiatives or knowledge.
Help on correctly describing the mapping of data to physical
and cognitive stimuli, as in Section~\ref{perceptual},
will be highly appreciated.
We might share and consider other supporting resources of our
research, e.g. those in Section~\ref{other}, upon
interest.

\subsection{Acknowledgments}
FAPESP (project 2017/05838-3); ICMC/USP and UFABC researchers;
the open source and free software communities that
made these developments possible.
